15th International Satisfiability Modulo Theories Competition (SMT-COMP 2020): Rules and Procedures

### 2021-05-01 rules/rules21.tex
various changes

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2020.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2020 aim specifically at making the competition more
manageable to run, as both the popularity of the competition and the
benchmark library have grown over time.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf The option \akey{:print-success} is explicitly set to true or false.}
    Previous competitions set this option to \akey{true} for the incremental track.
    In addition, this competition will set the option to \akey{false} for all
    other tracks.

    \rationale{According to the standard the default value of
      \akey{:print-success} is true.  So a conforming solver would
      unnecessarily print \akey{success} after each command that needs
      to be stored and skipped by the post-processors.
      Additionally, solvers can use this option as indication whether
      incremental checking is desired.}

@@

  \item {\bf TODO LIFT? Limit the Number of Solvers.}
    This year solver development teams may only submit more than one
    entry if they are substantially different.  A justification must
    be provided for the difference.  We strongly encourage the teams
    to keep the number of solvers per team per category at at most
    two.

    \rationale{The organizers wish to keep the total run-time of the
      competition small, in case of unforeseen problems that require
      to rerun the whole competition.  The idea in allowing up to two
      submissions is to encourage the development of new, experimental
      techniques by allowing an ``alternative solver'' to be submitted
      while keeping the competition manageable.}

  \item {\bf TODO: Time Limit.} The time limit per solver/benchmark pair is
    anticipated to be at most 20 minutes in the \maintrack, \inctrack,
    \ucoretrack and \mvaltrack.
    \rationale{The time limit for the Main Track is
      reduced to 20 minutes (down from 40 minutes in the previous years),
      to make running the competition more manageable}

  \item {\bf Benchmark Selection.}
    This year we reduce the percentage of the benchmarks that are run in the competition.
    \rationale{The goal is to make running the competition more managable.}

@@

  \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
    divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the
    model validation track.  This year these will no longer be experimental.

@@

\header{Portfolio Solver.}
%
A \emph{portfolio solver} is a solver using a combination of two or
more sub-solvers, developed by different groups of authors, on the
same component or abstraction of the input problem.  For example, a
solver using one subsolver to solve the ground abstraction of a
quantified problem is allowed, while a solver using two or more
subsolvers from different groups of authors is not.
Porfolio solver are in general \textbf{not allowed}.
If you are unsure if your tool is a portfolio solver according to this
definition and you feel that it should be allowed contact the
organizers of the SMT-COMP for clarification.

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2020.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2020 aim specifically at making the competition more
manageable to run, as both the popularity of the competition and the
benchmark library have grown over time.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf The option \akey{:print-success} is explicitly set to
    true or false.}  Previous competitions set this option to
    \akey{true} for the incremental track.  In addition, this
    competition will set the option to \akey{false} for all other
    tracks.
    \rationale{According to the standard the default value of
      \akey{:print-success} is true.  So a conforming solver would
      unnecessarily print \akey{success} after each command that needs
      to be stored and skipped by the post-processors.  Additionally,
      solvers can use this option as indication whether incremental
      checking is desired.}

    We were asked to set the \akey{:incremental} option to true for
    the incremental track.  However this is problematic, because it is
    not a standard option and solvers may not support it.

@@

    Previously an unsound response for a benchmark did punish the
    score corresponding to the benchmark status.  We fix it to count
    errors to the score that correspond to the solver output, not the
    benchmark status.
    \rationale{If a solver returns \texttt{unsat} for a
      satisfiable benchmark, all other \texttt{unsat} responses of the
      solver are no longer trustworthy.  So it is the unsat score of
      the solver that must be punished.  The \texttt{sat} responses
      may still be trustworthy.  In the extreme case, a solver that
      always return \texttt{unsat} would a high error score for the
      unsat category under the new rules, and would get no points at
      all for the sat category.}

  \item {\bf Benchmark Selection.}
    This year we increase the percentage of the benchmarks that are run in the competition back to 50 \%.
    \rationale{We feel that increasing the number of benchmarks is managable and 50 \% is a more round number than 40 \%.}

@@

  \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
    divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the
    model validation track.  This year these will no longer be experimental.
    In addition, new experimental divisions QF\_UF, QF\_UFBV,
    QF\_UFIDL, QF\_UFLIA, QF\_UFLRA will be added.

@@

\header{Portfolio Solver.}
%
A \emph{portfolio solver} is a solver using a combination of two or
more sub-solvers, developed by different groups of authors, on the
same component or abstraction of the input problem.  For example, a
solver using one subsolver to solve the ground abstraction of a
quantified problem is allowed, while a solver using two or more
subsolvers from different groups of authors is not.
Portfolio solver are in general \textbf{not allowed}.
If you are unsure if your tool is a portfolio solver according to this
definition and you feel that it should be allowed contact the
organizers of the SMT-COMP for clarification.
